On the power of oritatami cotranscriptional folding with unary bead sequence\thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779 and JST Program to Disseminate Tenure Tracking System No.~6F36 granted to S.~Z.~F. and S.~S.}

### 2018-12-05 tt_theorem.tex
12/5 latest

	\node[above] at (180:1) {$p_1$};
	\node[left] at (-120:1) {$p_2$};
	\node[left] at (-60:1) {$p_3$};
	\node[left, shift=(-120:1)] at (-60:1) {$p_3$};

@@

Now let us verify the claim. 
Suppose $w[i]$ were stabilized by just one bond. 
There are three cases to be considered as depicted in Fig.~\ref{TTT_a3_w}, depending on the relative position of $w[i]$ to $w[i-2]$ and $w[i-1]$. 
Since $S[i] = b$, at least one of the four neighbors of $w[i-1]$ must be empty. 
If $w_3$ is free, then $w[i-2]$ must have used up all of its hands; otherwise, $w[i]$ would be stabilized also at $n_3$ nondeterministically, a contradiction. 
Thus, $\alpha + 2 = 5$ neighbors of $w[i-2]$, that is, all of its neighbors, must be occupied. 
Hence, $n_5$ is occupied. 
(All the remaining arguments are based on this ``merry-go-round'' occupation. This works only if the circle of radius 2 around $w[i-1]$ is free from the singular bead). 
In the same way, all the neighbors of $n_3$ turned out to be occupied in the clockwise order, but eventually, we would encounter a neighbor that is adjacent to also the point where $w[i]$ is supposed to go. 
Thus, $n_3$ must be occupied (in the left and middle cases). 
In the left case, $n_4$ is symmetric to $n_3$, and hence, it must be occupied, too. 
Since $S[i] = b$, $n_1$ or $n_2$ must be free; assume $n_1$ is. 
Going clockwise around $n_1$ implies that $n_{-1}$ is occupied, but the bead at $n_1$ has a free hand and would cause a nondeterminism.

@@

\begin{figure} [tb]
  \begin{center}
  \begin{tabular}{c c c}
 \begin{minipage}{0.3\hsize}
 \centering
    \begin{tikzpicture}
      \draw[white] (60:2) circle [radius=0.05];
      \node[above, white] at (60:2) {$n_adj$};

@@

@@

 	\node[right] at (0:1) {$n_0$};
	\node[below] at (-60:1) {$n_2$};
	\node[above] at (120:1) {$n_3$};
	\node[below] at (-120:1) {$n_4$};
	\node[above, shift=(60:1)] at (0:1) {$n_{-1}$};
	\node[above, shift=(60:1)] at (60:1) {$n_{-2}$};
	\node[above, shift=(60:1)] at (120:1) {$n_{-3}$};
	\node[below, shift=(180:1)] at (-120:1) {$n_5$};
    \end{tikzpicture}
    \end{minipage}

@@

 	\node[right] at (0:1) {$n_0$};
	\node[above] at (60:1) {$n_1$};
	\node[below] at (-60:1) {$n_2$};
	\node[below] at (-120:1) {$n_4$};
	\node[above, shift=(120:1)] at (60:1) {$n_{-1}$};
	\node[above, shift=(120:1)] at (120:1) {$n_{-2}$};
	\node[above, shift=(120:1)] at (180:1) {$n_{-3}$};
    \end{tikzpicture}
    \end{minipage}
    \end{tabular}
    \caption{All possible directions of $w[i]$: straight, obtuse, acute.}
    \label{TTT_a3_w}
  \end{center}
\end{figure}

>>>>

	\node[above] at (180:1) {$p_1$};
	\node[left] at (-120:1) {$p_2$};
	\node[left, shift=(-120:1)] at (-60:1) {$p_3$};
	\node[right] at (-60:1) {$p_4$};

@@

Now let us verify the claim. 
Suppose $w[i]$ were stabilized by just one bond. 
There are three cases to be considered as depicted in Fig.~\ref{TTT_a3_w}, depending on the relative position of $w[i]$ to $w[i-2]$ and $w[i-1]$. 
Since $S[i] = b$, at least one of the four neighbors of $w[i-1]$ must be empty. 
If $n_3$ is free, then $w[i-2]$ must have used up all of its hands; otherwise, $w[i]$ would be stabilized also at $n_3$ nondeterministically, a contradiction. 
Thus, $\alpha + 2 = 5$ neighbors of $w[i-2]$, that is, all of its neighbors, must be occupied. 
Hence, $n_5$ is occupied. 
(All the remaining arguments are based on this ``merry-go-round'' occupation. This works only if the circle of radius 2 around $w[i-1]$ is free from the singular bead). 
In the same way, all the neighbors of $n_3$ turned out to be occupied in the clockwise order, but eventually, we would encounter a neighbor that is adjacent to also the point where $w[i]$ is supposed to go. 
Thus, $n_3$ must be occupied (in the left and middle cases). 
In the left case, $n_4$ is symmetric to $n_3$, and hence, it must be occupied, too. 
Since $S[i] = b$, $n_1$ or $n_2$ must be free; assume $n_1$ is. 
Going clockwise around $n_1$ implies that $n_{-1}$ is occupied, but the bead at $n_1$ has a free hand and would cause a nondeterminism.

@@

\begin{figure} [tb]
  \begin{center}
  \begin{tabular}{c c c}
 \begin{minipage}{0.3\hsize}
 \centering
    \begin{tikzpicture}
      \draw[white] (60:2) circle [radius=0.05];
      \node[right, white] at (60:2) {$n_{adj}$};

@@

    \begin{minipage}{0.3\hsize}
    \centering
     \begin{tikzpicture}
	\node[right, shift=(60:1), white] at (60:1) {$n_{adj}$};
      \fill[shift=(180:1)] (0,0) circle [radius=0.1];
      \fill[shift=(180:0)] (0,0) circle [radius=0.1];

@@

 	\node[right] at (0:1) {$n_0$};
	\node[below] at (-60:1) {$n_2$};
	\node[above] at (120:1) {$n_3$};
	\node[below] at (-120:1) {$n_4$};
	\node[above, shift=(60:1)] at (0:1) {$n_{-1}$};
	\node[below, shift=(180:1)] at (-120:1) {$n_5$};
    \end{tikzpicture}
    \end{minipage}

@@

 	\node[right] at (0:1) {$n_0$};
	\node[right] at (60:1) {$n_1$};
	\node[below] at (-60:1) {$n_2$};
	\node[below] at (-120:1) {$n_4$};
	\node[right, shift=(120:1)] at (60:1) {$n_{-1}$};
    \end{tikzpicture}
    \end{minipage}
    \end{tabular}
    \caption{All possible directions of $w[i]$: straight, obtuse, acute.}
    \label{TTT_a3_w}
  \end{center}
\end{figure}
